---
title: "p8105_hw5_ak4123"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(purrr)

set.seed(1)

```

#Question 1
```{r question 1}

files = list.files("./data", full.names = TRUE)
data_files = 
  tibble(
  treatment =  str_detect(files, "con"),
  participant_id = str_extract(files, "\\d+(?=.csv)"),
  data = map(.x = files, ~read.csv(.x))
  )
data_files =
  data_files %>% 
  unnest %>% 
  mutate(treatment = case_when(treatment == TRUE ~ "Control",
                         treatment == FALSE ~ "Experimental")
  ) %>% 
  gather(key = "week", week_1:week_8, value = "value") %>% 
  mutate(week = as.numeric(str_extract(week, "\\d"))) %>% 
  arrange(treatment, participant_id)
data_files

ggplot(data_files, aes(x = week, y = value, color = participant_id)) + 
  facet_grid(.~treatment) + 
  geom_line() + 
 viridis::scale_color_viridis(
      discrete = TRUE,
      name = "participant id"
    ) +
    labs(
      x = "week",
      y = "value",
      title = "Observed Values by Treatment Group over Time"
    ) +
    theme_bw()

```
The major difference between the control and experimental groups is that the observed values of the experimental group are significantly higher than in the control group. Also, there is more of an upward trend over time in the experimental group, whereas the controls tended to have an end value at week 8 around the same as the value measured in week 1. 
#Question 2

***DESCRIBE THE RAW DATA HERE:
``` {r question 2}
homicides = read_csv("./data-homicides/homicide-data.csv") %>% 
  janitor::clean_names()

homicides %>%
  nrow()
homicides %>% 
  ncol()
homicides %>% 
  select(victim_first) %>% 
  head(1)
homicides %>% 
  select(victim_last) %>% 
  head(1)
homicides %>% 
  select(victim_age) %>% 
  head(1)
homicides %>% 
  select(city) %>% 
  head(1)
homicides %>% 
  select(state) %>% 
  head(1)
homicides %>% 
  select(disposition) %>% 
  head(1)
```
ADD DESCRIPTION IN LINE

```{rest of question 2}
homicides = 
  homicides %>% 
  mutate(city_state = paste(city, state, sep = ", "))

total_homicides = 
  homicides %>% 
  group_by(city_state) %>% 
  summarize(n()) %>% 
  summarize(unsolved_homicides = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest"))

baltimore_homicides =
  total_homicides %>% 
  filter(city_state == "Baltimore, MD")
  
baltimore_prop = 
  prop.test(x = baltimore_homicides$unsolved_homicides,
            n = baltimore_homicides$total_homicides) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)

baltimore_prop$estimate
baltimore_prop$conf.low
baltimore_prop$conf.high
```
For the city of Baltimore, MD the estimate the proportion of homicides that are unsolved is . 